Model-Based Goal Recognition with Unknown Domain Models

### 2019-01-24 doc/ijcai-19-goalRecognition/goalRecognition.tex
adding old content to the ijcai19 paper on goal recognition

\subsection{Model-Based Goal Recognition}
We formalize the {\em goal recognition} task following the standard  formalization of Ram\'irez and Geffner for plan recognition~\cite{ramirez2012plan}.

The {\em model-based goal recognition} is a classification task defined by a tuple $\tup{P,\mathcal{O}}$, where:
\begin{itemize} 
\item $P=\tup{F,A,I,G[\cdot]}$ is a planning problem where $G[\cdot]$ is a set of possible goals.
\item $\mathcal{O}(\tau)$ is an observation of a trajectory $\tau(\pi,P)$ produced by the execution of an unknown plan $\pi$ that solves the planning problem $P$.
\end{itemize}

Following the {\em naive Bayes classifier}, the {\em solution} to the {\em model-based goal recognition} task is the subset of goals in $G[\cdot]$ that maximizes this expression.

@@

The {\em Plan recognition as planning} approach shows how to compute estimates of the $P(\mathcal{O}|g)$ likelyhood using an off-the-shelf classical planner. Recent works show that faster, but less accurate estimates, of this $P(\mathcal{O}|g)$ likelyhood can also be computed using relaxations of the classical planning task.

>>>>

{\em Goal recognition} is a particular classification task in which each class represents a different goal and each example is an observation of an agent acting to achieve one of that goals. Following the {\em naive Bayes classifier}, the {\em solution} to the {\em goal recognition} task is the subset of goals in $G[\cdot]$ that maximizes this expression.

@@

The {\em Plan recognition as planning} approach shows how to compute estimates of the $P(\mathcal{O}|g)$ likelyhood leveraging the action model of the observed agent and an off-the-shelf classical planner. Recent works show that faster, but less accurate estimates, of this $P(\mathcal{O}|g)$ likelyhood can also be computed using relaxations of the classical planning tasks~\cite{pereira2017landmark}.
